Generalized Algebraic Data Types in Haskell

### 2013-05-21 gadt.tex
Minor edits to make it build
Signed-off-by: Edward Z. Yang <ezyang@mit.edu>

Generalized algebraic data types (GADTs) is a feature of functional programming languages that generalizes ordinary algebraic data types by permitting value constructors to return specific types. This article is a tutorial about GADTs in Haskell programming language as they are implemented by the Glasgow Haskell Compiler (GHC) as a language extension. GADTs are widely used in practice: for domain-specific embedded languages, for generic programming, for ensuring program correctness and in other cases. The article describes these use cases with small GADT programs and also describes usage of GADTs in Yampa, a Haskell library.

>>>>

Generalized algebraic data types (GADTs) are a feature of functional programming languages which generalize ordinary algebraic data types by permitting value constructors to return specific types. This article is a tutorial about GADTs in Haskell programming language as they are implemented by the Glasgow Haskell Compiler (GHC) as a language extension. GADTs are widely used in practice: for domain-specific embedded languages, for generic programming, for ensuring program correctness and in other cases. The article describes these use cases with small GADT programs and also describes usage of GADTs in Yampa, a Haskell library.
